---
title: "DATA PRODUCTS 1"
author: "VIDUSHI ANAND"
date: "February 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Developing Data Products Assignment 1

This Markdown is the first assignment for the course Developing Data Products.In this document I have created a web page using R Markdown that features a map created with Leaflet. The map coordinates have been taken from google for my current location.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
 

## leaflet


```{r pressure, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% addTiles() 
my_map <- my_map %>% addMarkers(lat=28.5602807, lng= 77.33818084810235, popup="My Location")
my_map
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
